An Incomplete Overview of Some Applications of Game Theory to Patient Flow

### 2014-05-14 paper.tex
Replaced tikz version of first FIGURA

The best known work applying Game Theory to Healthcare is Roth's Noble prize winning work \cite{Roth}.
This work uses matching game algorithms to match medical interns to hospitals.
The purpose of this paper is to discuss some work relevant to a different area of healthcare: congestion.

@@

\begin{figure}[!hbtp]
\begin{center}
\includegraphics[width=.7\textwidth]{./Images/Hospital_Choices.pdf}
\end{center}
\caption{Routing patients from $m$ hospitals to $n$ services.}\label{fig:choices}
\end{figure}

@@

As a utility function $w_i$ is taken to be the mean waiting time in an $M/M/c$ queue.
From known results on convexity of this measure \cite{} the following optimisation problems can be solved straightforwardly so as to be able to obtain the PoA for a given instance:

>>>>

The best known work applying Game Theory to Healthcare is Roth's Noble prize winning work \cite{roth_redesign_1999}.
This work uses matching game algorithms to match medical interns to hospitals.
The purpose of this paper is to discuss some work relevant to a different area of healthcare: congestion.

@@

\begin{figure}[!hbtp]
\begin{center}

\begin{tikzpicture}
\node (S1) at (0,0) [circle, draw=blue, fill=blue!5] {$\Lambda_1$};
\node (S2) at (0,-2) [circle, draw=blue, fill=blue!5] {$\Lambda_2$};
\node (S3) at (0,-4)  {$\vdots$};
\node (S4) at (0,-6) [circle, draw=blue, fill=blue!5] {$\Lambda_m$};

\node (B1) at (-5,0) [circle, draw=blue, fill=red!5] {$\beta_1$};
\node (B2) at (-5,-2) [circle, draw=blue, fill=red!5] {$\beta_2$};
\node (B3) at (-5,-4)  {$\vdots$};
\node (B4) at (-5,-6) [circle, draw=blue, fill=red!5] {$\beta_m$};

\node (F1) at (5,-1) [circle, draw=blue, fill=red!5] {$w_1$};
\node (F3) at (5,-3)  {$\vdots$};
\node (F2) at (5,-5) [circle, draw=blue, fill=red!5] {$w_n$};

\draw [->, red] (S1) -- (B1);
\draw [->, red] (S2) -- (B2);
\draw [->, red] (S4) -- (B4);

\draw [->, red] (S1) -- (F1) node [midway, above, sloped, black] (TextNode) {$\lambda_{11}$};
\draw [->, red] (S1) -- (F2) node [midway, above, sloped, black] (TextNode) {$\lambda_{1n}$};
\draw [->, red] (S2) -- (F1) node [midway, above, sloped, black] (TextNode) {$\lambda_{21}$};
\draw [->, red] (S2) -- (F2) node [near start, above, sloped, black] (TextNode) {$\lambda_{2n}$};
\draw [->, red] (S4) -- (F1) node [near start, above, sloped, black] (TextNode) {$\lambda_{m1}$};
\draw [->, red] (S4) -- (F2) node [midway, above, sloped, black] (TextNode) {$\lambda_{mn}$};

\node at (-2.5,-7) {Balk};
\node at (2.5,-7) {Seek Service};
\end{tikzpicture}
\end{center}
\caption{Routing patients from $m$ hospitals to $n$ services.}\label{fig:choices}
\end{figure}

@@

As a utility function $w_i$ is taken to be the mean waiting time in an $M/M/c$ queue.
From known results on convexity of this measure \cite{lee_note_1983} the following optimisation problems can be solved straightforwardly so as to be able to obtain the PoA for a given instance:
